\LARGE \bf Autonomous Object Manipulation using a Soft Planar Grasping Manipulator

### 2015-10-12 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex

We thank the reviewer for this comment. We revised the exposition to highlight the differences between the two approaches. The algorithm in [12] is about planning the motion of a soft arm without a gripper through a maze at a centerline while taking the arms bulging shape as a trapezoidal into account. The approach does not work for approaching objects with the manipulator including a gripper, because a tip trajectory for successfully moving towards the object is not known, but needs to be generated. That trajectory needs to avoid pushing the object away with the manipulator trunk when approaching it with the soft gripper at its end. In this paper we present an algorithm for approaching an object by following along concentric lines, which are further and further decreasing in size until object size is achieved. The non-linear optimization is finding tangent poses along these lines using non-linear optimization and then follows down those concentric lines, which implicitly guarantees the arms pose to stay convex – since the circles are convex themselves.

\subsection{Optimization Constraints}
\textit{Section 4.2 Is the optimization function over or underconstrained? Will you always find a solution? What happens if you don’t find a solution?}

The optimization function is only over-constrained if we have to achieve a pose outside of the reachable workspace. Otherwise it is well-constrained. The system optimizes for the quadratic cost of having high curvatures. A solution is not found only if the target object pose is not within the reachable workspace of the arm, that means of the object was placed by the user outside of the workspace. The arm’s workspace can easily be calculated and added this formula to the paper. This workspace check is performed before doing any further calculations.

\subsection{Solver Details}
\textit{Section 4.2 par 1., Provide the speed of the optimization solver as well as the solver used.}
The nonlinear optimization problem was implemented using Matlab’s Optimization Toolbox with the function calls fmincon, which finds the minimum of a constrained nonlinear multivariable function. Sequential Quadratic Programming was used as the solver with a relative upper bound of $2 \times 10^{-3}$ on the magnitude of the constraint functions. The lower bound on the size of a step was given by $1 \times 10^{-6}$. The solver takes about 1\unit{s} on a regular PC to solve for all waypoints from start to finish. We included this information in the paper.
\subsection{Convexity as Constraint?}
\textit{Section 4.2 par 1. “…while its null space maintains a convex shape, bending away from the object”. Is the convexity actually a hard constraint on the solver? How much does this depend on your specific task and the orientation of the arm/gripper combo?}
When solving for a tangent gripper pose in CCW direction along the green concentric circles, this is implicitly the constraint for convexity. The algorithm proposed is task-specific as to picking up an object on a plane without pushing it away prematurely. We also added a note to the manuscript to clarify this.
\subsection{Algorithm Numbering}
\textit{Section 4.3 The text describing Algorithm 1 would be well suited to have numbered sections that could help the reader understand at which location in the Algorithm the text is referring to.}
Thank you for this advise. The way the algorithmic environment was set up in this document, it is not trivial to add line numbering to it. Instead we clarified the description of the algorithmic steps within the manuscript better, it should not require the line numbers anymore. 
\subsection{Object Details}
\textit{Section 5.2 What is the object weight? What is the object radius?}
The object has a weight of 18\unit{g} and a diameter of 3.3\unit{cm}. We added this info to the manuscript.
\subsection{Task Execution Speed}
\textit{Figure 9: What is the time/speed of the task?}
Depending on where the object is placed, the arm takes between 17-35\unit{s} to approach it. The task of moving back to the bin takes between 10-20\unit{s}. We added this data to the paper. 

@@

Depending on where the object is placed, the arm takes between 17-35\unit{s} to approach it. The task of moving back to the bin takes between 10-20\unit{s}. We added this data to the paper. 
%
\subsection{Additional References}
\textit{Lack of references (Some covered in DeVolder2010):
De Volder, Michaël, and Dominiek Reynaerts. "Pneumatic and hydraulic microactuators: a review." Journal of Micromechanics and microengineering20.4 (2010): 043001.
Ikuta, Koji, Hironobu Ichikawa, and Katsuya Suzuki. "Safety-active catheter with multiple-segments driven by micro-hydraulic actuators." Medical Image Computing and Computer-Assisted Intervention—MICCAI 2002. Springer Berlin Heidelberg, 2002. 182-191.
J. Xiao and R. Vatcha, “Real-time adaptive motion planning for a continuum manipulator,” Proc. IROS 2010, pp. 5919–5926, Oct. 2010.
J. Li and J. Xiao, “A general formulation and approach to constrained, continuum manipulation,” Adv. Robot., no. July 2015, pp. 1–11, 2015.}
Thank you for your comments, we added these references to the introduction section of the paper.

### 2015-10-12 experimental_results.tex
response to reviewer 1 comments, half way

\subsection{Repeated Grasp Experiments}
We performed 25 experimental grasp-and-place trials at various positions to demonstrate the capabilities and repeatability of our system.
The results of all the trials are shown in Figure~\ref{fig:allTestsOverlaid}.
One representative approach, grasp, and retract move is shown in Figure~\ref{fig:oneTrialVsTime}.
In 23 of 25 experimental trials, the manipulator successfully achieved the task of grasping an object and bringing it to a bin location shown in red.
The object was placed five times on each of the five points marked on the board.
The markers only serve as a reference point for the user to place the object roughly at the same point at every repetition.
The user's placing accuracy is not important to the algorithm, \rkk{since the tracking system newly registers the position of the object every time it is placed.}
The five points were chosen to approximately represent the major portion of the manipulator's reachable workspace.
As long as the root of the gripper stops so that the object is located within the capture region, the gripper will pick it up through its sweeping closing motion. The capture region is shown in grey in Figure~\ref{fig:grasp_uncertainty}.

@@

The unsuccessful trials happened due to stick-slip friction between the roller bearings and the table surface.
Our kinematic modeling does not account for this non-linear behavior, which acts as a disturbance and can lead to failure to arrive at the next waypoint.
To be more specific, in one of the trials, the robot slowed down too much before it almost reached its next waypoint and because of friction the arm halted to a full stop. 
The proportional gain of the curvature controller was not able to compensate for that small positional delta and since the relatively low saturation level of the integrator portion of the controller was saturated, the arm did not move to the next waypoint pose. 
It is to note, that the saturation level for the integrator is defined by a safety limit on the maximal inflation of the robotic arm.
In the other unsuccesful trial, the stick-slip friction also caused the arm to halt before a waypoint. The controller built up enough forcing due to inflation, so that the arm slipped over the close waypoint without having all of its single arm segment curvature within an acceptable epsilon.
The controller then tried to swing back to fulfill the missed waypoint, missed it again and that finally caused the whole arm to oscillate back-and-forth and eventually push the object off the table.
In one of the other trials, the grasp and return was successfully performed, but a small overshoot over the final bin location at the end of the return caused the arm to drop off the table, which could have been avoided if the table would have not been too small towards the right.
This outlier is shown in Figure~\ref{fig:allTestsOverlaid}.
Overall, the experiments show that the system was repeatably able to autonomously locate a randomly placed object within its workspace, plan the arm motions, and perform the task of grasping and placing the object.

@@

\begin{figure*}[htbp]
\begin{centering}
  \includegraphics[width=0.375\textwidth]{Figures/experimental_results/oneTrialVsTime.eps}
\includegraphics[width=0.30\textwidth]{figures/experimental_results/exp5a-4_sweep_to_object.jpg}
\includegraphics[width=0.31\textwidth]{figures/experimental_results/exp5a-4_sweep_to_bin.jpg}
  \caption{Left: A time series representation of an experimental grasp-and-place trial for an object located at point E. Here, the locally optimal planned manipulator configurations as well as planned sequential approach circles are shown as black dotted curves. The arm and gripper are shown in their experimentally determined configuration representations at 1 second intervals. The cyan configurations represent the manipulator prior to grasping the object, that is moving from its initial configuration to the object's location. The magenta configurations represent the manipulator after grasping the object, that is moving from the object's location back to the bin location shown in red. Right: A photograph of the arm moving from its initial pose to the object and from the object to the release location, respectively.}
\label{fig:oneTrialVsTime}
\end{centering}
\end{figure*}

>>>>

\subsection{Repeated Grasp Experiments}
We performed 25 experimental grasp-and-place trials at various positions to demonstrate the capabilities and repeatability of our system.
The results of all the trials are shown in Figure~\ref{fig:allTestsOverlaid}.
One representative approach, grasp, and retract move is shown in Figure~\ref{fig:oneTrialVsTime}.
In 23 of 25 experimental trials, the manipulator successfully achieved the task of grasping an object and bringing it to a bin location shown in red.
\rkk{The test object has a weight of 18\unit{g} and a diameter of 3.3\unit{cm}.}
The object was placed five times on each of the five points marked on the board.
The markers only serve as a reference point for the user to place the object roughly at the same point at every repetition.
The user's placing accuracy is not important to the algorithm, \rkk{since the tracking system newly registers the position of the object every time it is placed.}
The five points were chosen to approximately represent the major portion of the manipulator's reachable workspace.
As long as the root of the gripper stops so that the object is located within the capture region, the gripper will pick it up through its sweeping closing motion. The capture region is shown in grey in Figure~\ref{fig:grasp_uncertainty}.

@@

The unsuccessful trials happened due to stick-slip friction between the roller bearings and the table surface.
Our kinematic modeling does not account for this non-linear behavior, which acts as a disturbance and can lead to failure to arrive at the next waypoint.
To be more specific, in one of the trials, the robot slowed down too much before it almost reached its next waypoint and because of friction the arm halted to a full stop. 
The proportional gain of the curvature controller was not able to compensate for that small positional delta and since the relatively low saturation level of the integrator portion of the controller was saturated, the arm did not move to the next waypoint pose. 
It is to note, that the saturation level for the integrator is defined by a safety limit on the maximal inflation of the robotic arm.
In the other unsuccessful trial, the stick-slip friction also caused the arm to halt before a waypoint. The controller built up enough forcing due to inflation, so that the arm slipped over the close waypoint without having all of its single arm segment curvature within an acceptable epsilon.
The controller then tried to swing back to fulfill the missed waypoint, missed it again and that finally caused the whole arm to oscillate back-and-forth and eventually push the object off the table.
In one of the other trials, the grasp and return was successfully performed, but a small overshoot over the final bin location at the end of the return caused the arm to drop off the table, which could have been avoided if the table would have not been too small towards the right.
This outlier is shown in Figure~\ref{fig:allTestsOverlaid}.
Overall, the experiments show that the system was repeatably able to autonomously locate a randomly placed object within its workspace, plan the arm motions, and perform the task of grasping and placing the object.

@@

\begin{figure*}[htbp]
\begin{centering}
  \includegraphics[width=0.375\textwidth]{Figures/experimental_results/oneTrialVsTime.eps}
\includegraphics[width=0.30\textwidth]{figures/experimental_results/exp5a-4_sweep_to_object.jpg}
\includegraphics[width=0.31\textwidth]{figures/experimental_results/exp5a-4_sweep_to_bin.jpg}
  \caption{Left: A time series representation of an experimental grasp-and-place trial for an object located at point E. Here, the locally optimal planned manipulator configurations as well as planned sequential approach circles are shown as black dotted curves. The arm and gripper are shown in their experimentally determined configuration representations at 1 second intervals. The cyan configurations represent the manipulator prior to grasping the object, that is moving from its initial configuration to the object's location. \rkk{Depending on where the object is placed, the arm takes between 17-35\unit{s} to approach it.} The magenta configurations represent the manipulator after grasping the object, that is moving from the object's location back to the bin location shown in red. \rkk{This task of moving back to the bin takes between 10-20\unit{s}.} Right: A photograph of the arm moving from its initial pose to the object and from the object to the release location, respectively.}
\label{fig:oneTrialVsTime}
\end{centering}
\end{figure*}

### 2015-10-12 introduction.tex
response to reviewer 1 comments, half way

\subsection{Related Work}
There are several examples of soft grippers described in recent literature, we will mainly focus on fluidic-based systems. 
Deimel and Brock \cite{deimel2013compliant} developed a pneumatically actuated three-fingered hand made of reinforced silicone that is mounted to a hard robot and capable of grasping.
More recently, they have developed an anthropomorphic soft pneumatic hand capable of dexterous grasps, which is not mounted to a robot, but instead just held by a human \cite{deimel2014novel}. 
Ilievski et al. \cite{ilievski2011soft} create through a soft-lithography fabrication a pneumatic starfish-like gripper composed of an array of silicone chambers and a PDMS membrane.

>>>>

\subsection{Related Work}
\rkk{An overview of pneumatic and hydraulic microactuators has been provided by Volder et al. \cite{volder2010pneumatic}.} 
\rkk{Ikuta and Suzuki \cite{ikuta2002safety} developed a multiple-segment micro-hydraulic actuator that can be controlled open-loop within blood vessels.}
\rkk{Xiao and Vatcha\cite{xiao2010realtime} present simulation results of an online motion planner for a planar continuum manipulators.}
\rkk{ Li and Xiao \cite{li2015general} extend this work to present a more general formulation to constrained, continuum manipulation.}
There are \rkk{also} several examples of soft grippers described in recent literature, we will mainly focus on fluidic-based systems.
Deimel and Brock \cite{deimel2013compliant} developed a pneumatically actuated three-fingered hand made of reinforced silicone that is mounted to a hard robot and capable of grasping.
More recently, they have developed an anthropomorphic soft pneumatic hand capable of dexterous grasps, which is not mounted to a robot, but instead just held by a human \cite{deimel2014novel}. 
Ilievski et al. \cite{ilievski2011soft} create through a soft-lithography fabrication a pneumatic starfish-like gripper composed of an array of silicone chambers and a PDMS membrane.

### 2015-10-12 processing_control.tex
response to reviewer 1 comments, half way

The procedure first determines the manipulator's current tip pose $\mathbf{w}_t$ and the Euclidean distance $d_1$ between the tip and the object's center. 
\rkk{The arc length input to the arm's forward kinematics is the $N$-th element of the segment lengths $\mathbf{L}_{\textrm{meas}}$.}
Next, considering the object's radius $r_o$ and the gripper normal offset $\mathbf{g}_{\textrm{off}}$, the minimal tip transit distance $d_2$ is calculated. 
\rkk{The end effector offset $\mathbf{w}_{\textrm{off}}$ describes the distance from the root of the gripper, to an offset point close to the lower end of the gripper's palm. It is visualized in the top left corner of Fig.~\ref{fig:grasp-and-place-planner}.}
\rkk{The length} $\mathbf{g}_{\textrm{off}}$ represents the component of the end effector offset $\mathbf{w}_{\textrm{off}}$, which is normal to the end effector orientation. 
Also, the number of approach configurations $numMoves$ is determined as $\lfloor \frac{d_2}{\Delta d} \rfloor$, where $\Delta d$ is an allowable incremental distance. 
Using these parameters, approach radii $r_a$ are iteratively calculated and their corresponding locally optimal configurations are found using the \texttt{findOptimalConfig($r_a$)} procedure. 
This process is posed as a nonlinear optimization. 
Here, the objective function represents the summation of independently weighted manipulator curvatures and the constraints force the manipulator's tip to lie on and to be tangent to the approach circle. 
This process leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced in Algorithm~\ref{alg:planGrasp} for convenience.

>>>>

The procedure \rkk{\texttt{planGrasp()} in Algorithm \ref{alg:planGrasp}} first determines the manipulator's current tip pose $\mathbf{w}_t$ and the Euclidean distance $d_1$ between the tip and the object's center. 
\rkk{The arc length input to the arm's forward kinematics is the $N$-th element of the segment lengths $\mathbf{L}_{\textrm{meas}}$.}
\rkk{The end effector offset $\mathbf{w}_{\textrm{off}}$ describes the distance from the root of the gripper, to an offset point close to the lower end of the gripper's palm. It is visualized in the top left corner of Fig.~\ref{fig:grasp-and-place-planner}.}
\rkk{The length} $\mathbf{g}_{\textrm{off}}$ represents the component of the end effector offset $\mathbf{w}_{\textrm{off}}$, which is normal to the end effector orientation. 
The minimal tip transit distance $d_2$ is calculated by \rkk{considering the object's radius $r_o$ and the gripper normal offset $\mathbf{g}_{\textrm{off}}$.} 
Also, the number of approach configurations $numMoves$ is determined as $\lfloor \frac{d_2}{\Delta d} \rfloor$, where $\Delta d$ is an allowable incremental distance. 
Using these parameters, approach radii $r_a$ \rkk{shown by the green circles} are iteratively calculated and their corresponding locally optimal configurations are found using the \texttt{findOptimalConfig($r_a$)} procedure.

\rkk{The procedure \texttt{findOptimalConfig($r_a$)}} is posed as a nonlinear optimization \rkk{problem}. 
Here, the objective function represents the summation of independently weighted manipulator curvatures \rkk{$\boldsymbol{\kappa} - \boldsymbol{\kappa}_{\textrm{off}}$.} The optimization constraints \rkk{cause} the manipulator's tip to lie on and to be tangent to the approach circle. 
\rkk{The constraints also ensure that the manipulator segment curvatures do not exceed the single soft actuator limits.}
\rkk{Furthermore,} this \rkk{procedure} leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced \rkk{in the last section} of Algorithm~\ref{alg:planGrasp} for convenience.

\rkk{The nonlinear optimization problem was implemented using Matlab’s Optimization Toolbox with the function calls \emph{fmincon}, which finds the minimum of a constrained nonlinear multivariable function. Sequential Quadratic Programming was used as the solver with a relative upper bound of $2 \times 10^{-3}$ on the magnitude of the constraint functions. The lower bound on the size of a step was given by $1 \times 10^{-6}$. The solver takes about 1\unit{s} on a regular PC to solve for all waypoints from start to finish.}
